Music adaptation: Analysis (only first instances)

### 2022-10-14 analysis/onlyfirst.Rmd
update analysis for only first instances
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: 'Music adaptation: Analysis'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

Description: This is a summary of analysis comparing between baseline and test performance.

@@

@@

@@

```{r ioi}
# for each individual
dt_ioi$Articulation <- factor(dt_ioi$Articulation, c("Present", "Absent", "Baseline"))
dt_ioi$Dynamics <- factor(dt_ioi$Dynamics, c("Present", "Absent", "Baseline"))

ioi_trial <- dt_ioi[, .(N = .N, Mean = mean(IOI), SD = sd(IOI), CV = sd(IOI)/mean(IOI)), by = .(SubNr, TrialNr, Stimuli, Articulation, Dynamics, Category)]

@@

### Plot
#### Boxplot
```{r ioi-plot, fig.width = 6}
ggboxplot(ioi_trial, "Articulation", "Mean", color = "Dynamics", add = "jitter", facet.by = "SubNr", xlab = "Articulation", ylab = "IOIs (ms)", title = "IOI")
```

## 2. All - group

@@

```{r ioi-all-plot}
ggplot(ioi, aes(x = Articulation, y = Mean, color = Dynamics))+ 
  geom_boxplot(position = position_dodge2(preserve = "single")) +
  geom_point(position = position_dodge(0.75)) +
  theme_pubr()
#ggboxplot(ioi, "Articulation", "Mean", color = "Dynamics", add = "jitter", xlab = "Articulation", ylab = "IOIs (ms)", title = "IOI")
```

@@

```{r}
aov_ez(
  data = ioi[Category != "baseline"],
  id = "SubNr",
  dv = "Mean",
  within = c("Articulation", "Dynamics")
)
```

@@

pairs(emmeans(ioi_ca_all_aov, "Category"), adjust = "tukey")
```

@@

pairs(emmeans(ioi_ca_par_aov, "Category"), adjust = "tukey")
```

4) Variability

```{r}
aov_ez(
  data = ioi,
  id = "SubNr",
  dv = "SD",
  within = c("Category")
)
```

@@

```{r kot, echo = FALSE}
# for each individual
dt_kot$Articulation <- factor(dt_kot$Articulation, c("Present", "Absent", "Baseline"))
dt_kot$Dynamics <- factor(dt_kot$Dynamics, c("Present", "Absent", "Baseline"))

kot_trial <- dt_kot[Subcomponent1 == "Legato" | Subcomponent1 == "Staccato", .(N = .N, Mean = mean(KOT), SD = sd(KOT)), by = .(SubNr, TrialNr, Stimuli, Articulation, Dynamics, Category, Subcomponent1)]

@@

## 2. All - group

@@

```{r kot-all-plot, echo = FALSE}
ggplot(kot, aes(x = Articulation, y = Mean, color = Dynamics))+
  geom_boxplot(position = position_dodge2(preserve = "single")) +
  geom_point(position = position_dodge(0.75)) +
  facet_grid( ~ Subcomponent1, labeller = as_labeller(c("Legato" = "Legato/Forte", "Staccato" = "Staccato/Piano"))) +
  theme_pubr()

@@

```{r}
aov_ez(
  data = kot[Subcomponent1 == "Legato" & Category != "baseline"],
  id = "SubNr",
  dv = "Mean",
  within = c("Articulation", "Dynamics")
)
```
2) Category: All

@@

pairs(emmeans(leg_ca_all_aov, "Category"), adjust = "tukey")
```

@@

pairs(emmeans(leg_ca_par_aov, "Category"), adjust = "tukey")
```

@@

```{r}
aov_ez(
  data = kot[Subcomponent1 == "Staccato" & Category != "baseline"],
  id = "SubNr",
  dv = "Mean",
  within = c("Articulation", "Dynamics")
)
```

@@

```{r}
sta_ca_all_aov <- aov_ez(
  data = kot[Subcomponent1 == "Staccato"],
  id = "SubNr",
  dv = "Mean",
  within = c("Category")
)
sta_ca_all_aov

pairs(emmeans(sta_ca_all_aov, "Category"), adjust = "tukey")
```

@@

```{r}
sta_ca_par_aov <- aov_ez(
  data = kot[Subcomponent1 == "Staccato" & Category == "both" | Subcomponent1 == "Staccato" & Category == "dyn_only" | Subcomponent1 == "Staccato" & Category == "baseline"],
  id = "SubNr",
  dv = "Mean",
  within = c("Category")
)
sta_ca_par_aov

pairs(emmeans(sta_ca_par_aov, "Category"), adjust = "tukey")
```
# Dynamics
## 1. Individual

```{r vel, echo = FALSE}
# for each individual
dt_vel$Articulation <- factor(dt_vel$Articulation, c("Present", "Absent", "Baseline"))
dt_vel$Dynamics <- factor(dt_vel$Dynamics, c("Present", "Absent", "Baseline"))

vel_trial <- dt_vel[Subcomponent2 != "NA", .(N = .N, Mean = mean(Velocity), SD = sd(Velocity)), by = .(SubNr, TrialNr, Stimuli, Articulation, Dynamics, Category, Subcomponent2)]

@@

```{r vel-all-plot,  echo = FALSE}
ggplot(vel, aes(x = Dynamics, y = Mean, color = Articulation))+ 
  geom_boxplot(position = position_dodge2(preserve = "single")) +
  geom_point(binaxis = "y", stackdir = "center", position = position_dodge(0.75)) +
  facet_grid( ~ Subcomponent2, labeller = as_labeller(c("Forte" = "Forte/Legato", "Piano" = "Piano/Staccato"))) +
  theme_pubr()

@@

ggline(vel_seq, x = "RowNr", y = "Mean", add = "mean_se", position = position_dodge(.2), shape = "Category", color = "Category", xlab = "Note Nr", ylab = "Velocity (0-127)", title = "Velocity") + scale_x_continuous(breaks = seq(1,72,1))
```

@@

```{r}
aov_ez(
  data = vel[Subcomponent2 == "Forte" & Category != "baseline"],
  id = "SubNr",
  dv = "Mean",
  within = c("Articulation", "Dynamics")
)
```

@@

```{r}
for_ca_all_aov <- aov_ez(
  data = vel[Subcomponent2 == "Forte"],
  id = "SubNr",
  dv = "Mean",
  within = c("Category")
)
for_ca_all_aov

pairs(emmeans(for_ca_all_aov, "Category"), adjust = "tukey")
```

@@

```{r}
for_ca_par_aov <- aov_ez(
  data = vel[Subcomponent2 == "Forte" & Category == "both" | Subcomponent2 == "Forte" & Category == "art_only" | Subcomponent2 == "Forte" & Category == "baseline"],
  id = "SubNr",
  dv = "Mean",
  within = c("Category")
)
for_ca_par_aov

pairs(emmeans(for_ca_par_aov, "Category"), adjust = "tukey")
```

@@

```{r}
aov_ez(
  data = vel[Subcomponent2 == "Piano" & Category != "baseline"],
  id = "SubNr",
  dv = "Mean",
  within = c("Articulation", "Dynamics")
)
```
2) Category: All

```{r}
pia_ca_all_aov <- aov_ez(
  data = vel[Subcomponent2 == "Piano"],
  id = "SubNr",
  dv = "Mean",
  within = c("Category")
)
pia_ca_all_aov

pairs(emmeans(pia_ca_all_aov, "Category"), adjust = "tukey")
```

@@

```{r}
pia_ca_par_aov <- aov_ez(
  data = vel[Subcomponent2 == "Piano" & Category == "both" | Subcomponent2 == "Piano" & Category == "art_only" | Subcomponent2 == "Piano" & Category == "baseline"],
  id = "SubNr",
  dv = "Mean",
  within = c("Category")
)
pia_ca_par_aov

pairs(emmeans(pia_ca_par_aov, "Category"), adjust = "tukey")
```

@@

```{r vel-diff, echo = FALSE}
# for each individual
dt_vel_diff$Articulation <- factor(dt_vel_diff$Articulation, c("Present", "Absent", "Baseline"))
dt_vel_diff$Dynamics <- factor(dt_vel_diff$Dynamics, c("Present", "Absent", "Baseline"))

vel_diff_trial <- dt_vel_diff[Subcomponent2 == "FtoP" | Subcomponent2 == "PtoF", .(N = .N, Mean = mean(Diff), SD = sd(Diff)), by = .(SubNr, TrialNr, Stimuli, Articulation, Dynamics, Category, Subcomponent2)]

@@

```{r vel-diff-all-plot,  echo = FALSE}
ggplot(vel_diff, aes(x = Dynamics, y = Mean, color = Articulation))+ 
  geom_boxplot(position = position_dodge2(preserve = "single")) +
  geom_point(position = position_dodge(0.75)) +
  facet_grid( ~ Subcomponent2, labeller = as_labeller(c("FtoP" = "FtoP/PtoF", "PtoF" = "PtoF/StoL"))) +
  theme_pubr()

@@

```{r}
aov_ez(
  data = vel_diff[Subcomponent2 == "FtoP" & Category != "baseline"],
  id = "SubNr",
  dv = "Mean",
  within = c("Articulation", "Dynamics")
)
```

@@

```{r}
ftop_ca_all_aov <- aov_ez(
  data = vel_diff[Subcomponent2 == "FtoP"],
  id = "SubNr",
  dv = "Mean",
  within = c("Category")
)
ftop_ca_all_aov

pairs(emmeans(ftop_ca_all_aov, "Category"), adjust = "tukey")
```

@@

```{r}
ftop_ca_par_aov <- aov_ez(
  data = vel_diff[Subcomponent2 == "FtoP" & Category == "both" | Subcomponent2 == "FtoP" & Category == "art_only" | Subcomponent2 == "FtoP" & Category == "baseline"],
  id = "SubNr",
  dv = "Mean",
  within = c("Category")
)
ftop_ca_par_aov

pairs(emmeans(ftop_ca_par_aov, "Category"), adjust = "tukey")
```

@@

```{r}
aov_ez(
  data = vel_diff[Subcomponent2 == "PtoF" & Category != "baseline"],
  id = "SubNr",
  dv = "Mean",
  within = c("Articulation", "Dynamics")
)
```

@@

```{r}
ptof_ca_all_aov <- aov_ez(
  data = vel_diff[Subcomponent2 == "PtoF"],
  id = "SubNr",
  dv = "Mean",
  within = c("Category")
)
ptof_ca_all_aov

pairs(emmeans(ptof_ca_all_aov, "Category"), adjust = "tukey")
```

@@

```{r}
ftop_ca_par_aov <- aov_ez(
  data = vel_diff[Subcomponent2 == "FtoP" & Category == "both" | Subcomponent2 == "FtoP" & Category == "art_only" | Subcomponent2 == "FtoP" & Category == "baseline"],
  id = "SubNr",
  dv = "Mean",
  within = c("Category")
)
ftop_ca_par_aov

pairs(emmeans(ftop_ca_par_aov, "Category"), adjust = "tukey")
```

>>>>

---
title: 'Music adaptation: Analysis (only first instances)'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

Description: This is a summary of analysis which only include the performance with the first instance of each student (category).

@@

## Experimental Design
Note: Here, we only look at the first instance of each student (category).

- Independent variables: Articulation (2 levels: Present or Absent) x Dynamics (2 levels: Present or Absent)
- Dependent variables: Interonset intervals (IOIs), Key-overlap time (KOT), Key velocity (KV) and KV Difference

1. Main predictions ([preregistration](https://osf.io/qbzwt))

- If students performed the piece without articulation (i.e., only dynamics is implemented in the recordings), participants should exaggerate articulation more (i.e., producing longer legato and shorter staccato).
- If students performed the piece without dynamics (i.e., only articulation is implemented in the recordings), participants should exaggerate dynamics more (i.e., producing louder forte and softer piano).
- If students performed the piece without articulation and dynamics (i.e., neither articulation nor dynamics is implemented in the recordings), participants should exaggerate both articulation and dynamics more.

2. Excluded participants

- NA

3. Stats packages

- [afex](https://github.com/singmann/afex) for ANOVAs

@@

### TrialNr and Stimuli

```{r}
# select only performances for the first instance of each student (category)
info <- dt_ioi[, .(N = .N), by = .(SubNr, TrialNr, Stimuli, Category)]
info

first <- function(data, new_data){
  for (subnr in unique(info$SubNr)){
    for (category in unique(info[SubNr == subnr]$Category)){
      trials <- unique(info[SubNr == subnr & Category == category]$TrialNr)
      current <- data[SubNr == subnr & Category == category & TrialNr == min(trials)]
      new_data <- rbind(new_data, current)
    }
  }
  return(new_data)
}

dt_ioi_first <- data.table() 
dt_ioi_first <- first(dt_ioi, dt_ioi_first)

dt_kot_first <- data.table()
dt_kot_first <- first(dt_kot, dt_kot_first)

dt_vel_first <- data.table()
dt_vel_first <- first(dt_vel, dt_vel_first)

dt_vel_diff_first <- data.table()
dt_vel_diff_first <- first(dt_vel_diff, dt_vel_diff_first)
```

@@

```{r ioi}
# for each individual
dt_ioi_first$Articulation <- factor(dt_ioi_first$Articulation, c("Present", "Absent", "Baseline"))
dt_ioi_first$Dynamics <- factor(dt_ioi_first$Dynamics, c("Present", "Absent", "Baseline"))

ioi_trial <- dt_ioi_first[, .(N = .N, Mean = mean(IOI), SD = sd(IOI), CV = sd(IOI)/mean(IOI)), by = .(SubNr, TrialNr, Stimuli, Articulation, Dynamics, Category)]

@@

```{r ioi-plot, fig.width = 6}
ggboxplot(ioi_trial, "Articulation", "Mean", color = "Dynamics", add = "jitter", facet.by = "SubNr", xlab = "Articulation", ylab = "IOIs (ms)", title = "IOI")
```

## 2. Group

@@

```{r ioi-all-plot}
ggplot(ioi, aes(x = Articulation, y = Mean, color = Dynamics)) +
  geom_boxplot(outlier.shape = NA, position = position_dodge2(preserve = "single")) +
  geom_point(position = position_jitterdodge(jitter.width = 0.25), alpha = 0.5) + labs(y = "IOI (ms)", title = "IOI") +
  theme_pubr()

#ggboxplot(ioi, "Articulation", "Mean", color = "Dynamics", add = "jitter", xlab = "Articulation", ylab = "IOIs (ms)", title = "IOI")
```

@@

```{r}
ioi_all_aov <- aov_ez(
  data = ioi[Category != "baseline"],
  id = "SubNr",
  dv = "Mean",
  within = c("Articulation", "Dynamics"),
  detailed = TRUE
)

ioi_all_aov$anova_table
pairs(emmeans(ioi_all_aov, ~Dynamics|Articulation), adjust = "tukey")
```

@@

ioi_ca_all_aov$anova_table
pairs(emmeans(ioi_ca_all_aov, "Category"), adjust = "tukey")
```

@@

ioi_ca_par_aov$anova_table
pairs(emmeans(ioi_ca_par_aov, "Category"), adjust = "tukey")
```

<!-- 4) Variability -->

<!-- ```{r} -->
<!-- var_stats <- aov_ez( -->
<!--   data = ioi, -->
<!--   id = "SubNr", -->
<!--   dv = "SD", -->
<!--   within = c("Category") -->
<!-- ) -->

<!-- var_stats$anova_table -->
<!-- ``` -->

@@

```{r kot, echo = FALSE}
# for each individual
dt_kot_first$Articulation <- factor(dt_kot_first$Articulation, c("Present", "Absent", "Baseline"))
dt_kot_first$Dynamics <- factor(dt_kot_first$Dynamics, c("Present", "Absent", "Baseline"))

kot_trial <- dt_kot_first[Subcomponent1 == "Legato" | Subcomponent1 == "Staccato", .(N = .N, Mean = mean(KOT), SD = sd(KOT)), by = .(SubNr, TrialNr, Stimuli, Articulation, Dynamics, Category, Subcomponent1)]

@@

## 2. Group

@@

```{r kot-all-plot, echo = FALSE}
ggplot(kot[Subcomponent1 == "Legato"], aes(x = Articulation, y = Mean, color = Dynamics)) +
  geom_boxplot(outlier.shape = NA, position = position_dodge2(preserve = "single")) +
  geom_point(position = position_jitterdodge(jitter.width = 0.25), alpha = 0.5) +
  labs(y = "KOT (ms)", title = "KOT - Legato") +
  theme_pubr()

ggplot(kot[Subcomponent1 == "Staccato"], aes(x = Articulation, y = Mean, color = Dynamics)) +
  geom_boxplot(outlier.shape = NA, position = position_dodge2(preserve = "single")) +
  geom_point(position = position_jitterdodge(jitter.width = 0.25), alpha = 0.5) +
  labs(y = "KOT (ms)", title = "KOT - Staccato") +
  theme_pubr()

@@

```{r}
leg_all_aov <- aov_ez(
  data = kot[Subcomponent1 == "Legato" & Category != "baseline"],
  id = "SubNr",
  dv = "Mean",
  within = c("Articulation", "Dynamics")
)

leg_all_aov$anova_table
pairs(emmeans(leg_all_aov, ~Dynamics|Articulation), adjust = "tukey")
```

@@

leg_ca_all_aov$anova_table
pairs(emmeans(leg_ca_all_aov, "Category"), adjust = "tukey")
```

@@

leg_ca_par_aov$anova_table
pairs(emmeans(leg_ca_par_aov, "Category"), adjust = "tukey")
```

@@

```{r}
sta_all_aov <- aov_ez(
  data = kot[Subcomponent1 == "Staccato" & Category != "baseline"],
  id = "SubNr",
  dv = "Mean",
  within = c("Articulation", "Dynamics")
)

sta_all_aov$anova_table
pairs(emmeans(sta_all_aov, ~Dynamics|Articulation), adjust = "tukey")
```

@@

```{r}
sta_ca_all_aov <- aov_ez(
  data = kot[Subcomponent1 == "Staccato"],
  id = "SubNr",
  dv = "Mean",
  within = c("Category")
)

sta_ca_all_aov$anova_table
pairs(emmeans(sta_ca_all_aov, "Category"), adjust = "tukey")
```

@@

```{r}
sta_ca_par_aov <- aov_ez(
  data = kot[Subcomponent1 == "Staccato" & Category == "both" | Subcomponent1 == "Staccato" & Category == "dyn_only" | Subcomponent1 == "Staccato" & Category == "baseline"],
  id = "SubNr",
  dv = "Mean",
  within = c("Category")
)

sta_ca_par_aov$anova_table
pairs(emmeans(sta_ca_par_aov, "Category"), adjust = "tukey")
```

# Dynamics
## 1. Individual

```{r vel, echo = FALSE}
# for each individual
dt_vel_first$Articulation <- factor(dt_vel_first$Articulation, c("Present", "Absent", "Baseline"))
dt_vel_first$Dynamics <- factor(dt_vel_first$Dynamics, c("Present", "Absent", "Baseline"))

vel_trial <- dt_vel_first[Subcomponent2 != "NA", .(N = .N, Mean = mean(Velocity), SD = sd(Velocity)), by = .(SubNr, TrialNr, Stimuli, Articulation, Dynamics, Category, Subcomponent2)]

@@

```{r vel-all-plot,  echo = FALSE}
ggplot(vel[Subcomponent2 == "Forte"], aes(x = Dynamics, y = Mean, color = Articulation))+ 
    geom_boxplot(outlier.shape = NA, position = position_dodge2(preserve = "single")) +
  geom_point(position = position_jitterdodge(jitter.width = 0.25), alpha = 0.5) +
  labs(y = "Key Velocity (0-127)", title = "KV - Forte") +
  theme_pubr()

ggplot(vel[Subcomponent2 == "Piano"], aes(x = Dynamics, y = Mean, color = Articulation))+ 
    geom_boxplot(outlier.shape = NA, position = position_dodge2(preserve = "single")) +
  geom_point(position = position_jitterdodge(jitter.width = 0.25), alpha = 0.5) +
  labs(y = "Key Velocity (0-127)", title = "KV - Piano") +
  theme_pubr()

@@

ggline(vel_seq, x = "RowNr", y = "Mean", add = "mean_se", position = position_dodge(.2), shape = "Category", color = "Category", xlab = "Note Nr", ylab = "Key Velocity (0-127)", title = "KV") + scale_x_continuous(breaks = seq(1,72,1))
```

@@

```{r}
for_all_aov <- aov_ez(
  data = vel[Subcomponent2 == "Forte" & Category != "baseline"],
  id = "SubNr",
  dv = "Mean",
  within = c("Articulation", "Dynamics")
)

for_all_aov$anova_table
pairs(emmeans(for_all_aov, ~Articulation|Dynamics), adjust = "tukey")
```

@@

```{r}
for_ca_all_aov <- aov_ez(
  data = vel[Subcomponent2 == "Forte"],
  id = "SubNr",
  dv = "Mean",
  within = c("Category")
)

for_ca_all_aov$anova_table
pairs(emmeans(for_ca_all_aov, "Category"), adjust = "tukey")
```

@@

```{r}
for_ca_par_aov <- aov_ez(
  data = vel[Subcomponent2 == "Forte" & Category == "both" | Subcomponent2 == "Forte" & Category == "art_only" | Subcomponent2 == "Forte" & Category == "baseline"],
  id = "SubNr",
  dv = "Mean",
  within = c("Category")
)

for_ca_par_aov$anova_table
pairs(emmeans(for_ca_par_aov, "Category"), adjust = "tukey")
```

@@

```{r}
pia_all_aov <- aov_ez(
  data = vel[Subcomponent2 == "Piano" & Category != "baseline"],
  id = "SubNr",
  dv = "Mean",
  within = c("Articulation", "Dynamics")
)

pia_all_aov$anova_table
pairs(emmeans(pia_all_aov, ~Articulation|Dynamics), adjust = "tukey")
```

```{r}
pia_ca_all_aov <- aov_ez(
  data = vel[Subcomponent2 == "Piano"],
  id = "SubNr",
  dv = "Mean",
  within = c("Category")
)

pia_ca_all_aov$anova_table
pairs(emmeans(pia_ca_all_aov, "Category"), adjust = "tukey")
```

@@

```{r}
pia_ca_par_aov <- aov_ez(
  data = vel[Subcomponent2 == "Piano" & Category == "both" | Subcomponent2 == "Piano" & Category == "art_only" | Subcomponent2 == "Piano" & Category == "baseline"],
  id = "SubNr",
  dv = "Mean",
  within = c("Category")
)

pia_ca_par_aov$anova_table
pairs(emmeans(pia_ca_par_aov, "Category"), adjust = "tukey")
```

@@

```{r vel-diff, echo = FALSE}
# for each individual
dt_vel_diff_first$Articulation <- factor(dt_vel_diff_first$Articulation, c("Present", "Absent", "Baseline"))
dt_vel_diff_first$Dynamics <- factor(dt_vel_diff_first$Dynamics, c("Present", "Absent", "Baseline"))

vel_diff_trial <- dt_vel_diff_first[Subcomponent2 == "FtoP" | Subcomponent2 == "PtoF", .(N = .N, Mean = mean(Diff), SD = sd(Diff)), by = .(SubNr, TrialNr, Stimuli, Articulation, Dynamics, Category, Subcomponent2)]

@@

```{r vel-diff-all-plot,  echo = FALSE}
ggplot(vel_diff[Subcomponent2 == "FtoP"], aes(x = Dynamics, y = Mean, color = Articulation))+ 
  geom_boxplot(outlier.shape = NA, position = position_dodge2(preserve = "single")) +
  geom_point(position = position_jitterdodge(jitter.width = 0.25), alpha = 0.5) +
  labs(y = "KV Difference (-127-127)", title = "KV Difference - Forte to Piano") +
  theme_pubr()

ggplot(vel_diff[Subcomponent2 == "PtoF"], aes(x = Dynamics, y = Mean, color = Articulation))+ 
  geom_boxplot(outlier.shape = NA, position = position_dodge2(preserve = "single")) +
  geom_point(position = position_jitterdodge(jitter.width = 0.25), alpha = 0.5) +
  labs(y = "KV Difference (-127-127)", title = "KV Difference - Piano to Forte") +
  theme_pubr()

@@

```{r}
ftop_all_aov <- aov_ez(
  data = vel_diff[Subcomponent2 == "FtoP" & Category != "baseline"],
  id = "SubNr",
  dv = "Mean",
  within = c("Articulation", "Dynamics")
)

ftop_all_aov$anova_table
pairs(emmeans(ftop_all_aov, ~Articulation|Dynamics), adjust = "tukey")
```

@@

```{r}
ftop_ca_all_aov <- aov_ez(
  data = vel_diff[Subcomponent2 == "FtoP"],
  id = "SubNr",
  dv = "Mean",
  within = c("Category")
)

ftop_ca_all_aov$anova_table
pairs(emmeans(ftop_ca_all_aov, "Category"), adjust = "tukey")
```

@@

```{r}
ftop_ca_par_aov <- aov_ez(
  data = vel_diff[Subcomponent2 == "FtoP" & Category == "both" | Subcomponent2 == "FtoP" & Category == "art_only" | Subcomponent2 == "FtoP" & Category == "baseline"],
  id = "SubNr",
  dv = "Mean",
  within = c("Category")
)

ftop_ca_par_aov$anova_table
pairs(emmeans(ftop_ca_par_aov, "Category"), adjust = "tukey")
```

@@

```{r}
ptof_all_aov <- aov_ez(
  data = vel_diff[Subcomponent2 == "PtoF" & Category != "baseline"],
  id = "SubNr",
  dv = "Mean",
  within = c("Articulation", "Dynamics")
)

ptof_all_aov$anova_table
pairs(emmeans(ptof_all_aov, ~Articulation|Dynamics), adjust = "tukey")
```

@@

```{r}
ptof_ca_all_aov <- aov_ez(
  data = vel_diff[Subcomponent2 == "PtoF"],
  id = "SubNr",
  dv = "Mean",
  within = c("Category")
)

ptof_ca_all_aov$anova_table
pairs(emmeans(ptof_ca_all_aov, "Category"), adjust = "tukey")
```

@@

```{r}
ptof_ca_par_aov <- aov_ez(
  data = vel_diff[Subcomponent2 == "PtoF" & Category == "both" | Subcomponent2 == "PtoF" & Category == "art_only" | Subcomponent2 == "FtoP" & Category == "baseline"],
  id = "SubNr",
  dv = "Mean",
  within = c("Category")
)

ptof_ca_par_aov
pairs(emmeans(ftop_ca_par_aov, "Category"), adjust = "tukey")
```
